---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pipfaker

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to provide users who would like to use (or generate) *fake* [PIP](https://pip.worldbank.org/) data in several formats (raw or cache) and distribution types (micro, group, bin or imputed).

## Installation

You can install the development version of pipfaker from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("PIP-Technical-Team/pipfaker")
```

## Example

This is a basic example which shows you how to use a fake PIP data set:

```{r example}
library(pipfaker)
## basic example code

micro_cache_pip <- fk_cache_micro

mean_welf <- mean(micro_cache_pip$welfare_ppp, w = micro_cache_pip$weight)
mean_welf
```

## For `pipapi`

This package can be used to create fake data to test `pipapi`. There are two approaches:

### Using `fk_pip_ref()` (recommended)

`fk_pip_ref()` takes a reference PIP folder and creates a synthetic copy that mirrors its structure. It synthesises `survey_data` and `lineup_data` files using quantile-remapping (preserving weighted means per area/reporting level), copies `_GROUP`/`_BIN` files directly, and copies `_aux`, `estimations`, and root files verbatim. The `pct` argument controls the fraction of rows to generate (e.g. `0.1` for 10%).

#### Sequential (default) mode:

```{r pipapi_ref, eval = FALSE}
# Synthesise from a reference folder at 10% sample size
fk_pip_ref(
  input_path  = "E:/PIP/pipapi_data/20240627_2017_01_02_PROD",
  output_path = "path/to/output",
  pct         = 0.1
)

# Full-size synthetic copy (default pct = 1)
fk_pip_ref(
  input_path  = "E:/PIP/pipapi_data/20240627_2017_01_02_PROD",
  output_path = "path/to/output"
)
```

#### Parallel mode:

For large reference folders, use parallel processing to speed up synthesis of `survey_data` and `lineup_data` files. This requires the `future` package and a configured plan.

```{r pipapi_ref_parallel, eval = FALSE}
library(future)

# Set a parallel plan (e.g., multisession with 4 workers)
plan(multisession, workers = 4)

# Synthesise with parallel = TRUE
fk_pip_ref(
  input_path  = "E:/PIP/pipapi_data/20240627_2017_01_02_PROD",
  output_path = "path/to/output",
  pct         = 0.1,
  parallel    = TRUE
)

# Reset to sequential plan
plan(sequential)
```

### Using `fk_pip()` (legacy)

`fk_pip()` can generate fake data either from a reference folder or using the bundled fake datasets included in this package. If `input_path` is not provided, `fk_pip()` uses the pre-built fake data.

```{r pipapi_ex, eval = FALSE}
## Using input_path
# fk_pip(output_path = ".", input_path = "E:/PIP/pipapi_data/20240627_2017_01_02_PROD")

## Without input_path (using bundled fake data)
# fk_pip(output_path = ".")
```
